Hydra Battles and Cie

### 2021-07-12 doc/part-hydras.tex
Remove a buggy subdirectory
The implementation of multiplication in ordinals/OmegaOmega is buggy.
We save the files in branch FixOmegaOmega and temporarily remove them from master.

\section{Other ordinal notations}

\begin{project}
The directory \texttt{theories/OmegaOmega} contains an ad-hoc formalization of $\omega^\omega$, contributed by Pascal Manoury. Every ordinal $\alpha$ is represented by a list $l$ whose elements are the coefficients of $\omega$ in  the Cantor normal form of $\alpha$ (in reverse order). For instance, the ordinal 
$\omega^{8}\times 5 + \omega^{6}\times 8 + \omega^2\times 10 + \omega + 7$ is represented by the list \texttt{[5;0;8;0;0.0;10,1,7]}.

 Develop this representation and compare it with the other ordinal notations.

>>>>

\section{Other ordinal notations}
%%% TODO : Fix the multiplication function in branch FixOmegaOmega

% \index{hydras}{Projects}

% \begin{project}
% The directory \texttt{theories/OmegaOmega} contains an ad-hoc formalization of $\omega^\omega$, contributed by Pascal Manoury. Every ordinal $\alpha$ is represented by a list $l$ whose elements are the coefficients of $\omega$ in  the Cantor normal form of $\alpha$ (in reverse order). For instance, the ordinal 
% $\omega^{8}\times 5 + \omega^{6}\times 8 + \omega^2\times 10 + \omega + 7$ is represented by the list \texttt{[5;0;8;0;0.0;10,1,7]}.

%  Develop this representation and compare it with the other ordinal notations.

% \end{project}
